They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-05 presentation.qmd
shift up cod win series prop

>>>>

```{r}
summarize_cod_win_prop_after_x_wins_y_rounds <- function(k) {
  stopifnot((k >= 2) & (k <= 5))

  probs_nx_k <- crossing(
    n_rounds = 7L:11L,
    round = 1L:10L
  ) |> 
    filter(round <= n_rounds) |> 
    mutate(
      prior_p = 6L / n_rounds,
      expected_poststreak_p = map2_dbl(
        n_rounds, prior_p, 
        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
      )
    )

  cols <- sprintf('won_prior_round%d', 2:k)
  col_syms <- syms(cols)
  cod_round_streaks_after_x <- cod_round_streaks |> 
    drop_na(!!!col_syms) |> 
    count(n_rounds, round, win_round, won_prior_round1, !!!col_syms, sort = TRUE)

  cod_round_win_prop_after_x_wins |> 
    group_by(n_rounds, round) |> 
    mutate(
      total = sum(n),
      prop = n / total
    ) |> 
    ungroup() |> 
    filter(win_round) |> 
    select(n_rounds, round, n, total, prop) |> 
    arrange(n_rounds, round) |> 
    inner_join(
      probs_nx_k,
      by = c('n_rounds', 'round')
    ) |> 
    nest(data = -c(n_rounds, round)) |> 
    mutate(
      gt_p_value = map_dbl(
        data, 
        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
          broom::tidy() |>
          pull(p.value)
      ),
      lt_p_value = map_dbl(
        data, 
        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
          broom::tidy() |>
          pull(p.value)
      )
    ) |> 
    unnest(data)
}

cod_round_win_prop_after_x_wins_y_rounds <- tibble(win_streak = 2L:4L) |> 
  mutate(
    data = map(win_streak, summarize_cod_win_prop_after_x_wins_y_rounds)
  ) |> 
  unnest(data)
save_qs(cod_round_win_prop_after_x_wins_y_rounds)
```
